---
title: "statistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(lubridate)
library(tidyverse)

```


This vignette explains the different possibilities of the facepager package to find out more about the Facepager query itself.
As with all other packages you'll have to install the package and load the library first.

```{r setup}
# library(devtools)
# install_github("strohne/datavana/facepager")
library(facepager)

# Load example data
example <- read_csv2(system.file("extdata", "exampledata.csv", package = "facepager"))

```


Now you can access the various functions that allow you to examine your Facepager collection in more detail.


### Get status details of the query with `fp_status()`

With `fp_status()` you can get a first overview of your query and its results.

* How many nodes were queried via which Facepager module (e.g. Twitter or Facebook) and which endpoint (e.g. "search/tweets" or "page-id/posts")?

* For how many nodes was the query successful ("fetched(200)")?

* And how many nodes actually contain data ("data")?

```{r}
fp_status(example)
```



### Get requests per minute with `fp_timing()`

Especially if you are conducting surveys over a long period of time, it can be useful to get an overview over time as well. With `fp_timing()` you get details and plots about the time distribution of the requests.

* When did the survey start?

* When was it finished?

* How long did it last (in hours, minutes, seconds)?

* How many queries were sent per day?

```{r}
fp_timing(example)
```
