---
title: "Get Started with Epigraf Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{epigraf_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  message = FALSE, 
  warning = FALSE
)
```

## Why using Epigraf package? 

The Epigraf package aims to make data work with [Epigraf](https://epigraf.inschriften.net/) easier. 
Therefore it provides functions preparing data for import into epigraf article format.  

More is yet to come. 

## Installation 

```{r}
library(devtools)
install_github("strohne/datavana/epigraf")
```

## A simple example I 
The following example shows how to convert any text into epigraf article format. 
```{r}
library(tidyverse)
library(epigraf)

# Creating example data 
post <- tibble(
    id=1,
    project="Import",
    caption="My first text",
    content="Words are letters with glue")

# Converting data into epigraf article 
epidata <- epi_text2article(post)

# Display 
epidata

```


## A simple example II 
The following example shows how to convert a social media dataset into an Epigraf import file. The social media dataset follows the canoncial structure described on the project page.

```{r, eval=TRUE}
library(tidyverse)
library(epigraf)

# Load example data
threads <- read_csv2(system.file("extdata", "threads.csv", package = "epigraf"))

# Replace user names
threads <- sm_pseudonyms(threads)

# Convert to epi format
threads <- sm_canonical2epi(threads)

# Clean HTML content
threads <- sm_cleanhtml(threads, content)

# Display 
threads

```
